---
title: "zf_sm_deduplication_code"
output: pdf_document
---
title: "Deduplication_code"
output: pdf_document
---

Load packages
```{r}
rm(list= ls())
library(tidyverse) 
library(synthesisr) 
library(tidystringdist) 
library(bibliometrix)
```


Load in CSV file includes scopus, wos, pubmed and cochrane
```{r}
dat <- read.csv("zf_sm_all_database.csv")
dim(dat) # 2539 21 
```

Remove all punctuation and extra white spaces

```{r}
dat$title2 <- str_replace_all(dat$title,"[:punct:]","") %>% 
  str_replace_all(.,"[ ]+", " ") %>% 
  tolower()

```


Remove exact titles 
```{r}
dat2 <- distinct(dat, title2, .keep_all = TRUE) # select records with unique titles (removes exact duplicates)
dim(dat2) # 1827 22
```


Removing partial matches in titles 

```{r}
duplicates_string <- find_duplicates(dat2$title2, method = "string_osa", to_lower = TRUE, rm_punctuation = TRUE, threshold = 7)
```

Manually review titles to confirm they are duplicates 
```{r}
manual_checks <- review_duplicates(dat2$title, duplicates_string)
view(manual_checks)
```

Manually override some duplicates as unique 

```{r}
new_duplicates <- override_duplicates(duplicates_string, 40)
view(new_duplicates)
dat3 <- extract_unique_references(dat2, new_duplicates)
dim(dat3) 
names(dat3)
```

Drop columns "title2" and "n_duplicates"

```{r}
dat4 <- select(dat3, -c(title2,n_duplicates))
dim(dat4)
```


Save de-duplicated file

```{r}
write.csv(dat4, "zf_sm_abstracts_for_screening_deduplicated.csv")
write_refs(dat4, format = "bib", file = "zf_sm_abstracts_for_screening_deduplicated.bib")
```
