---
title: "zf_sm_code"
authors: "Kyle Morrison, Yefeng Yang, Manuela Santana, Malgorazata Lagisz and, Shinichi Nakagawa"
output: html_document
date: "2023-03-01"
---

Mapping the Behavioral Impacts of Pesticide Exposure on Zebrafish: A Systematic Evidence Map and Bibliometric Analysis

In this Rmarkdown we provide the following workflow:

- Objective 1.	To investigate the types of pesticides and pesticide classes, both in terms of chemical and target, that have been used in experiments examining the effects of pesticide exposure on zebrafish behaviour.

- Objective 2.	To identify the specific behaviours that have been investigated in pesticide exposure experiments that use zebrafish as a model.

- Objective 3.	To identify similarities and differences in research patterns and terminology across different disciplines.

- Objective 4. To examine how are authors connected between countries and how is the literature connected between and within disciplines. 

```{r setup, , results="hide"}

knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(tidyverse,
               here,
               stringr,
               knitr,
               formatR,
               forcats,
               ggplot2,
               hrbrthemes,
               patchwork,
               bibliometrix,
               igraph)
```


All extracted data is stored in five separate **.csv** files representing different aspects of the data (extracted via structured predefined Google Forms - one per table). 

Bibliographic data records are exported from Scopus (including cited references field) in .bib format and locally saved as **scopus.bib**.    

```{r load data}
bib <- read_csv(here("data", "zf_sm_bibliometrics.csv"), skip = 0)
sd <- read_csv(here("data","zf_sm_study_details.csv"), skip = 0)
pd <- read_csv(here("data", "zf_sm_pesticide_details.csv"), skip = 0)
pdo <-read_csv(here("data","zf_sm_pesticide_dosage.csv"), skip = 0)
bd <- read_csv(here("data", "zf_sm_behaviour_details.csv"), skip = 0)
```

